\section{Technical Data}

\subsection{General / Dimensions / Weights}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Housing] aluminum-profile framework\\
				 acrylic glass              \\
				 integrated LED lighting
  \item[Positioning system] extruder head mounted on belt driven H-frame (X/Y-axis) \\
                            screw driven print table (Z-axis) \\
                            semi-automatic three-point print bed leveling
  \item[3D printing technology] Fused Filament Fabrication (FFF)
  \item[Length] 800mm
  \item[Width] 	600mm
  \item[Height] 800mm
  \item[Weight] 49kg (empty)
  \item[Connection cable] 1.000mm w. Schuko plug and IEC connector
  \item[Network] Ethernet 10/100, RJ45
\end{description}


\subsection{Temperatures}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Extrusion temperature] max. +500\degree C
  \item[Print bed temperature] max. +130\degree C
  \item[Print chamber temperature] max. +70\degree C
\end{description}


\subsection{Hot ends}

Nozzles available in 0.35, 0.5, 0.75mm and 1.00mm bore diameter. By factory default, the left/right extruders
are equipped with a 0.35/0.5mm nozzle.


\subsection{Print}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Print volume] 200x185x280mm (10.4 liter)
  \item[Extruder head] dual extruder with two separate extruder nozzles for multi-colored  
                       and/or multi-material printing
  \item[Print bed] exchangeable 210x210mm PEI/carbon composite sheet 
  \item[Minimum layer resolution] 0.1mm
  \item[Positioning accuracy] $\pm$0.1mm
  \item[Approx. Tolerance] $\pm$0.2mm
\end{description}


\subsection{Material}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Printable materials] ABS, PLA, HIPS, PVA, PC, PA12, PET
  \item[Filament diameter] 2.85$\pm$0.1mm
  \item[Available filament qty.] 0.75kg spool (200x55mm) \\
                                 2.30kg spool (296x100mm)
\end{description}


\subsection{Power and Electronics}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Power consumption (total)] approx. 800W
  \item[Power supply unit] 1050W, 100 … 240V(AC) 
                           input with power plug and main switch \\
                           13-6.5A \\
                           50/60Hz \\
                           12V(DC) connector panel
  \item[Drives] 3x 1.2A stepper motor (XYZ positioning drives)  \\
                2x 1.2A planetary gear drive stepper motor (extruder drives)
  \item[Positioning step-width axes ]X=0.028mm \\
                                     Y=0.019mm \\
                                     Z=0.003mm
  \item[Hot ends ]12V, 40W integrated heating element per hot end
  \item[Print bed heating ]170W wired silicone heating pad
  \item[Chamber heating ]4x 170W heating resistor (two per heating element)
  \item[Chamber lighting ]2x 4W LED array, 6.500K
  \item[Stand-alone operating module ]integrated capacitive 10\textquotedbl touchscreen controller
  \item[Integrated computer ]UDOO Quad Single Board Computer (Quad core 1GHz CPU)
  \item[Machine control ]RADDS v1.5 3D Printer Driver Shield
  \item[Load switching ]3x High Current Solid State Relais
  \item[Fans ] 3x 119x119x25mm, 12V, 140m\textsuperscript{3}/h axial fan
                  (heat chamber circulation and cooling system)
\end{description}


\subsection{Sensors}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Limit switch H-frame (X/Y) and print table (Z)] magnetic hall endstops
  \item[Filament end recognition] mechanic limit switch
  \item[Temperature sensors hot ends ] 800\degree C thermocouple
  \item[Temperature sensors print table, print chamber] 300\degree C thermistors
\end{description}


\subsection{Closed loop water cooling system}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Pump] 12V(DC) circulation pump with integrated compensation reservoir
  \item[Throughput] approx. 210l/h
  \item[Radiator] 120mm full copper radiator
  \item[Fan] see \emph{electronics}
  \item[Coolant] Innovatek Protect IP ready-to-use
  \item[Coolant qty.] approx. 250ml
\end{description}

\subsection{Ambient conditions}

\begin{description}[style=multiline,leftmargin=6cm,font=\normalfont]
  \item[Operating temperature] +18\degree C … +27\degree C
  \item[Storage temperature] +5\degree C … +35\degree C
  \item[Rel. air humidity] max. 70\%
  \item[Setup site] no excessive formation of dust (e.g. near woodworks, CNC machining
                    centers)
\end{description}